---
format: 
  gfm: default
  html: default
bibliography: grateful-refs.bib
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAPID <img src='https://raw.githubusercontent.com/adafede/sapid/main/man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/adafede/sapid/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/adafede/sapid/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/adafede/sapid/graph/badge.svg)](https://app.codecov.io/gh/adafede/sapid)
[![r-universe badge](https://adafede.r-universe.dev/sapid/badges/version?&color=blue&style=classic)](https://adafede.r-universe.dev/sapid)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.14616395.svg)](https://doi.org/10.5281/zenodo.14616395)
<!-- badges: end -->

A **S**trategy to **A**nalyze **P**lant Extracts Taste **I**n **D**epth.

⚠️ This repository is not maintained and will not be except for extreme interest.
It has just been opened for the sake of transparency.

## Installation

As the package is not (yet) available on CRAN, you will need to install with:

``` r
install.packages(
  "sapid",
  repos = c(
    "https://adafede.r-universe.dev",
    "https://taxonomicallyinformedannotation.r-universe.dev",
    "https://bioc.r-universe.dev",
    "https://cloud.r-project.org"
  )
)
```

## Main Citations

### SAPID

Article: <https://doi.org/10.1016/j.crfs.2025.101043>

According to which steps you used, please give credit to the authors of the tools/resources used.

### mzmine

General: <https://doi.org/10.1038/s41587-023-01690-2>

### SIRIUS

General: <https://doi.org/10.1038/s41592-019-0344-8>

- *CSI:FingerId*: <https://doi.org/10.1073/pnas.1509788112>
- *ZODIAC*: <https://doi.org/10.1038/s42256-020-00234-6>
- *CANOPUS*: <https://doi.org/10.1038/s41587-020-0740-8>
- *COSMIC*: <https://doi.org/10.1038/s41587-021-01045-9>

### LOTUS

General: <https://doi.org/10.7554/eLife.70780>

⚠️ Do not forget to cite which version you used: <https://doi.org/10.5281/zenodo.5794106>

### ISDB

General: <https://doi.org/10.1021/acs.analchem.5b04804>

⚠️ Do not forget to cite which version you used: <https://doi.org/10.5281/zenodo.5607185>

### TIMA

General: <https://doi.org/10.3389/fpls.2019.01329>

⚠️ Do not forget to cite which version you used: <https://doi.org/10.5281/zenodo.5797920>

### Others

- NPClassifier: <https://doi.org/10.1021/acs.jnatprod.1c00399>

## Additional software credits

```{r, echo = FALSE, message = FALSE}
# Check if DESCRIPTION is in current dir
# Else `altdoc` will not find the dependencies
desc_path <- if (file.exists("DESCRIPTION")) {
  "."
} else {
  ".."
}
grateful::cite_packages(
  output = "table",
  out.dir = getwd(),
  path = desc_path
) |> 
  knitr::kable()
```
